Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-04-20 analysis/paper/shceof.Rmd
Mueve el abstract al principio
(por el word output)
Render PDF

bibstyle: spbasic
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      keep_tex: true
      # citation_package: "natbib"
      pandoc_args: ["--lua-filter=abstract-to-meta.lua"]
always_allow_html: true
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
 - \usepackage{lineno}
 - \linenumbers 
---

@@

----

>>>>

bibstyle: spbasic
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  # bookdown::word_document2: default    
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      keep_tex: true
      # citation_package: "natbib"
      pandoc_args: ["--lua-filter=abstract-to-meta.lua"]
always_allow_html: true
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
 - \usepackage{lineno}
 - \linenumbers 
---

@@
